\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{color}
\usepackage{soul}
\usepackage{hyperref}
\usepackage[backend=biber, style=ieee, url=false]{biblatex}
\usepackage{varioref}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{booktabs,caption}
\usepackage[flushleft]{threeparttable}
\renewcommand*{\bibfont}{\footnotesize}
\setlength{\biblabelsep}{\labelsep}
\setlength{\bibitemsep}{\IEEEbibitemsep}

\addbibresource{bibliography.bib}

\begin{document}

\title{Netflix QoExtension - A Tool for Conducting Ecologically Valid Experiments}

\author{\IEEEauthorblockN{Rafał Figlus}
\IEEEauthorblockA{\textit{rfiglus@agh.edu.pl} \\
\textit{AGH University of Science and
Technology, Institute of
Telecommunications
Kraków, Poland}\\
\\
}

%\and
%\IEEEauthorblockN{{}}
%\IEEEauthorblockA{\textit{} \\
%\textit{}\\
%\\}

%\and
%\IEEEauthorblockN{{}}
%\IEEEauthorblockA{\textit{} \\
%\textit{}\\
%\\}

%\and
%\IEEEauthorblockN{{}}
%\IEEEauthorblockA{\textit{} \\
%\textit{}\\
%\\}

%\and
%\IEEEauthorblockN{{}}
%\IEEEauthorblockA{\textit{} \\
%\textit{}\\
%\\}
}
\maketitle

\begin{abstract}
This paper describes Netflix QoExtension, a tool designed to facilitate ecologically valid experiments on the Netflix video streaming platform by enabling researchers to manipulate video quality of content selected by subjects based on their preferences. It enables researchers to create experiment sessions of varying duration, using any of the movies or TV shows available on Netflix.
\end{abstract}

\begin{IEEEkeywords}
Quality Of Experience; Netflix; Ecological Validity; Chrome Extension;
\end{IEEEkeywords}

\section{Introduction}
\label{sec:Introduction}
A significant portion of research in the field of Quality of Experience (QoE) relies on the fundamental methodology outlined in the ITU BT.500 \cite{BT.500-14} recommendation. Typical experiment consists of a series of video stimuli presented to the subject. After each stimulus quality score is collected from the subject and the process is repeated multiple times using numerous videos sharing similar or the same content. 

One critique of this approach is that subject being presented short video sequences repeatedly and asked for assessment may quickly become fatigued and lose focus. This can negatively impact the accuracy of the quality scores they provide. 
Additionally, this approach only focuses on the perceived video quality, and no other factors that may influence subject's overall QoE in a real-world setting are taken into account.
Therefore such experiment is not considered ecologically valid as it does not reflect real life conditions in which multimedia are consumed by users.

In order to propose more ecologically valid approach, that more closely mimics real-world conditions and therefore allows to examine what influences user's perception of video quality more accurately, we have developed a Netflix QoExtension.

\section{Overview}
\label{sec:Overview}
Entire tool can be described as several modules working together in order to execute pre-prepared scenario and collect experiment data. 
Tool is designed to work with Google Chrome web browser as it utilizes its API.
Minimal setup required to conduct experiment consists of a computer, monitor or TV set and mouse for the subject to submit quality scores. 
Tool was tested on Windows and macOS operating systems.


% Architecture section
\input{architecture.tex}

% Features section
\input{features.tex}


\printbibliography

\end{document}
